---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scCoco

<!-- badges: start -->
<!-- badges: end -->

Annotation of single cell clusters to brain regions using the common coordinate framework and ISH data from Allen brain atlas 

This package provides wrapper functions around the [cocoframer R package](https://github.com/AllenInstitute/cocoframer) that allows to query the [Allen brain atlas API](atlas.brain-map.org).


## Installation

Install scCoco using:

``` r
if (!require("remotes", quietly = TRUE))
    install.packages("remotes")
remotes::install_github("lsteuernagel/scCoco")
```

Depends on the cocoframer R package.

## Function overview

Load package:

```{r}
library(scCoco)
```


List of functions:

```{r}
sort(as.character(lsf.str("package:scCoco")))
```


Check the man pages for details!
